\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
\begin{document}

\section{Summary of System Variables}

\subsection{Discussion}

\begin{itemize}
    \item Fees should only be given to those who have actually issued nomins?
    \item How do we incentivise people to even transfer stuff.
    \item Utilisation ratio needs to have distinct parts. Number of escrowed curits is not quite the same as the number of issued nomins.
\end{itemize}

\subsubsection{Investment incentives}
Why would anyone buy curits in the first place? A potential buyer of curits has two avenues for making
money in Havven:

\paragraph{Capital gains due to the appreciation of curits.}
Presumably the currency will appreciate due to a demand for curits that is founded in the intrinsic
utility of a stablecoin. Speculators will of course be important players too, though.

\paragraph{Interest accrued from fees.}
If and when the price of curits stabilises, then this may be the only long term positive-expected
source of revenue. Ideally fees are set at a level where they are both high enough to be an incentive
for rent-seekers to hold curits in the long term (thus assuming the risk of providing collateral for
the system) and low enough not to be a disincentive for ordinary users to transact in nomins.
It is desirable, perhaps in a future world dominated by micropayments, for these fees to be
negligible for end users, while still being macroeconomically important for the system. 

\subsubsection{Fees}
There are a number of questions to be asked, and answered:
\begin{enumerate}
    \item What are fees for?
    \item When can fees be levied?
    \item Who gets those fees?
    \item What macroeconomic effect does this levy have as a coin travels through the system?
\end{enumerate}

\subsubsection{Liquidity}


\hfill

\subsection{Quantities of Interest}
\paragraph{Money Supply}
\begin{align*}
    C & \ && \text{(curits)} && \text{ : Quantity of curits, should be constant} \\
    C_e &= C \cdot U \ && \text{(curits)} && \text{ : Quantity of reserved curits, i.e. the value of tokens have been issued against } \\
    N &= \frac{U_a \cdot C \cdot P_c}{P_n} \ && \text{(nomins)} && \text{ : Quantity of nomins. This can float.}
\end{align*}
\\

\paragraph{Utilisation Ratios} We should work out a good level for \(U_{max}\).
\begin{align*}
    U &= \frac{P_n \cdot N}{C_e \cdot P_c} \ && \text{(dimensionless)} && \text{ : Empirical issuance ratio. } \\
    U_{max} & \ && \text{(dimensionless)} && \text{ : Targeted issuance ratio ceiling. Ideally, } 0 \leq U \leq U_max \leq 1
\end{align*}
\\

\paragraph{Prices} These values are important, with the goal of stabilising the nomin price.
\begin{align*}
    P_c & \ && (\frac{\text{\$}}{\text{curits}}) && \text{ : curit price} \\
    P_n & \ && (\frac{\text{\$}}{\text{nomins}}) && \text{ : nomin price} \\
    P_c' &= \alpha \cdot f(V_n, V_v) \cdot R && (\frac{\text{\$}}{\text{nomins} \cdot \text{seconds}}) && \text{ : R a risk term incorporating volatility? \#buyers - \#sellers?})
\end{align*}
\\

\paragraph{Fees}
\[F_x, F_i, F_r \ \text{(dimensionless) : transfer, issuance, redemption fees; these should be ratios, e.g. 0.1\%}\]
\\

\paragraph{Money Movement}
\begin{align*}
    V_n &= S_n \cdot N \ && (\frac{nomins}{seconds}) && \text{ : nomin transfer rate} \\
    V_v &= V_i + V_r \ && (\frac{curits}{seconds}) && \text{ : nomin} \leftrightarrow \text{curit conversion rate.} \\
    V_i &= (C - C_e) \cdot S_i \ && (\frac{curits}{seconds}) && \text{ : nomin issuance rate. Assumed to grow as there are more free curits in the system (actually should probably grow with the number of escrowed but unissued nomins).} \\
    V_r &= C_e \cdot S_r \ && (\frac{curits}{seconds}) && \text{ : rate at which curits are redeemed in return for nomins (which are burned). Assumed to grow proportionally with the number of escrowed curits.}
\end{align*}
\\

\paragraph{Microeconomic Variables} These should be defined as functions of \(P_n, P_c, \text{fees, etc.}\)
\begin{align*}
S_n \ && (\frac{1}{\text{seconds}}) && \text{ : average nomin spend rate} \\
S_i \ && (\frac{1}{\text{seconds}}) && \text{ : average issuance rate} \\
S_r \ && (\frac{1}{\text{seconds}}) && \text{ : average redemption rate}
\end{align*}

\end{document}
